Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$

### 2015-02-12 doc/HH4b_Documentation.tex
updated docs
Add boosted control plots to documentation

@@

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{|c||c||c|c|c|c||c|c|}
\hline
Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
\hline
b-tag    	& 1.516 &      102271         & 135255        & 42934  	&	202.9	&5.40E-6	& 0.157\\
jet $p_T,\eta$         & 0.723 &        3847      & 10676       & 5045 	&	122.7	&3.67E-5	& 0.282\\
di-jet $p_T$           	& 0.371&      553.7        & 1838	  & 926.0	&	22.45	&1.11E-4	& 0.352\\
di-jet $\Delta\eta$   & 0.336&       324.8       & 991.4 	  & 312.6		&	16.39	&2.04E-4	& 0.454\\
\hline
$m_H$ window   &0.190 &          7.632      & 13.60	  & 0.502	&	2.675	&7.78E-3	& 2.106\\
\hline
\end{tabular}
\end{center}
\caption{Table demonstrating the cutflow of an example resolved analysis applied to the full sample set.  $S/\sqrt{B}$ is given for HL-LHC luminosities.}
\label{tab:resCutflow}
\end{table}%

\subsection{Example boosted analysis}
Here we shall discuss an example boosted analysis. In this case \emph{Fatjet cuts} refers to the requirement of two $R=1$ anti-$k_T$ jets with $p_T>250$ GeV and $|\eta| < 2.5$. \emph{2 Subjets} requires two anti-$k_T$ $R=0.3$ subjects in each fat jet. \emph{b-Tagging} cuts those events in which the two hardest subjets are not successfully $b$-tagged. Here efficiency and mistag factors are applied for $b$ and $c$ jets as a function of subjet $p_T$. \emph{Mass-drop } requires that the two fat jets pass a BDRS mass-drop tagger with parameters $\mu = 0.67$ and $y_{\mathrm{cut}} = 0.09$. Finally \emph{$m_H$ window} only passes events where the two fat jet masses are within $15$ GeV of $m_H$. In Table~\ref{tab:boostedCutflow} we see the results of these cuts.
\begin{table}[htdp]
\begin{center}
\begin{tabular}{|c||c||c|c|c|c||c|c|}
\hline
Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
\hline
Fatjet cuts 			&2.802           	&3045 	& 1.13E6 &	4.57E7    &       9808  & 5.98E-8 &0.022 \\
2 Subjets  	&	2.740 	&2694	& 1.01E6	&	4.21E7 	&	9787  &6.35E-8 & 0.023\\
b-Tagging    			& 0.070		&39.76	& 296.9		&	352.9            &      7.586 & 1.00E-5& 0.145\\
Mass-drop  		& 0.068 		&36.84	& 256.0    	&	305.1            &	7.514 & 1.12E-4& 0.151 \\
%\hline
$m_H$ window       		&   0.045		& 2.134	& 10.83	& 	0.630            & 	0.438 & 3.20E-3& 0.658\\
\hline
\end{tabular}
\end{center}
\caption{Table demonstrating the cutflow of an example boosted analysis applied to the full sample set. $S/\sqrt{B}$ is given for HL-LHC luminosities.}
\label{tab:boostedCutflow}
\end{table}%

>>>>

\subsubsection{$bb$-jet rejection for the four hardest jets}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & After $bb$ rejection & \% selected  \\
\hline \hline
$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & & 7.467\% \\
\hline
$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & & 5.472\% \\
$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & & 0.0224\% \\
\hline
\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& & \multicolumn{1}{c}{}\\
\cline{1-3}
\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& & \multicolumn{1}{c}{}\\
\cline{1-3}
\end{tabular}
\end{center}
\caption{Summary of the $b$-tagging and $bb$-rejection cuts on the four leading jets.}\label{tab:TestbbTag}
\end{table}%

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\textwidth]{plots/histo_mfj1_preCut.pdf}
\includegraphics[width=0.49\textwidth]{plots/histo_mfj2_preCut.pdf}
\caption{Mass distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
\label{fig:mfj_boosted_pre}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj1_preCut.pdf}
\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj2_preCut.pdf}
\caption{$d_{12}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
\label{fig:split12_fj_boosted_pre}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj1_preCut.pdf}
\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj2_preCut.pdf}
\caption{$\tau_{21}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
\label{fig:tau21_fj_boosted_pre}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\textwidth]{plots/histo_mfj1.pdf}
\includegraphics[width=0.49\textwidth]{plots/histo_mfj2.pdf}
\caption{Mass distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
\label{fig:mfj_boosted_post}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj1.pdf}
\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj2.pdf}
\caption{$d_{12}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
\label{fig:split12_fj_boosted_post}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj1.pdf}
\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj2.pdf}
\caption{$\tau_{21}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
\label{fig:tau21_fj_boosted_post}
\end{center}
\end{figure}

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{|c||c||c|c|c|c||c|c|}
\hline
Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
\hline
\hline
b-tag    	& 1.516 &      102271         & 135255        & 42934  	&	202.9	&5.40E-6	& 0.157\\
jet $p_T,\eta$         & 0.723 &        3847      & 10676       & 5045 	&	122.7	&3.67E-5	& 0.282\\
di-jet $p_T$           	& 0.371&      553.7        & 1838	  & 926.0	&	22.45	&1.11E-4	& 0.352\\
di-jet $\Delta\eta$   & 0.336&       324.8       & 991.4 	  & 312.6		&	16.39	&2.04E-4	& 0.454\\
\hline
$m_H$ window   &0.190 &          7.632      & 13.60	  & 0.502	&	2.675	&7.78E-3	& 2.106\\
\hline
\end{tabular}
\end{center}
\caption{Table demonstrating the cutflow of an example resolved analysis applied to the full sample set.  $S/\sqrt{B}$ is given for HL-LHC luminosities.}
\label{tab:resCutflow}
\end{table}%

\subsection{Example boosted analysis}
Here we shall discuss an example boosted analysis. In this case \emph{Fatjet cuts} refers to the requirement of two $R=1$ anti-$k_T$ jets with $p_T>250$ GeV and $|\eta| < 2.5$. \emph{2 Subjets} requires two anti-$k_T$ $R=0.3$ subjects in each fat jet. \emph{b-Tagging} cuts those events in which the two hardest subjets are not successfully $b$-tagged. Here efficiency and mistag factors are applied for $b$ and $c$ jets as a function of subjet $p_T$. \emph{Mass-drop } requires that the two fat jets pass a BDRS mass-drop tagger with parameters $\mu = 0.67$ and $y_{\mathrm{cut}} = 0.09$. Finally \emph{$m_H$ window} only passes events where the two fat jet masses are within $15$ GeV of $m_H$. In Table~\ref{tab:boostedCutflow} we see the results of these cuts.
\begin{table}[htdp]
\begin{center}
\begin{tabular}{|c||c||c|c|c|c||c|c|}
\hline
Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
\hline
\hline
Fatjet cuts 			&2.802           	&3045 	& 1.13E6 &	4.57E7    &       9808  & 5.98E-8 &0.022 \\
2 Subjets  	&	2.740 	&2694	& 1.01E6	&	4.21E7 	&	9787  &6.35E-8 & 0.023\\
b-Tagging    			& 0.070		&39.76	& 296.9		&	352.9            &      7.586 & 1.00E-5& 0.145\\
Mass-drop  		& 0.068 		&36.84	& 256.0    	&	305.1            &	7.514 & 1.12E-4& 0.151 \\
\hline
$m_H$ window       		&   0.045		& 2.134	& 10.83	& 	0.630            & 	0.438 & 3.20E-3& 0.658\\
\hline
\end{tabular}
\end{center}
\caption{Table demonstrating the cutflow of an example boosted analysis applied to the full sample set. $S/\sqrt{B}$ is given for HL-LHC luminosities.}
\label{tab:boostedCutflow}
\end{table}%
